The Impact of Tax Policy Evolution on Economic Development and Income Inequality

### 2024-02-20 paper/paper.qmd
Add the gap analysis in introduction

>>>>

Despite the insightful exploration of tax equity in low- and middle-income countries by @article, there remains an underexplored area concerning the effectiveness of tax policy changes on the informal sector. While the shift from indirect to direct taxation is well-documented, its impact on the informal economy—a significant component of low- and middle-income countries—lacks a detailed analysis. Furthur studies should focus on evaluating how tax policy transitions influence the informal sector, thereby affecting overall economic development and equity.
